Project 2

### 2021-10-06 project_2.Rmd
Edited Fitzgerald corpus

```{r gutenberg_fitzgerald_works}
#finding texts by Fitzgerald on gutenberg
fitzgerald_text <- gutenberg_works(author == "Fitzgerald, F. Scott (Francis Scott)")
```

```{r gutenberg_fitzgerald_download}
#downloading all the texts found
fitzgerald_download <- fitzgerald_text %>% 
                      gutenberg_download(meta_fields = c("title", "author"))
```

@@

The_Sun_Also_Rises_Hemingway_Ernest <- read_delim("The Sun Also Rises_Hemingway, Ernest.txt", 
    delim = "\t", quote = "\\\"", escape_double = FALSE, 
    trim_ws = TRUE)
The_Sun_Also_Rises_Hemingway_Ernest <- The_Sun_Also_Rises_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Sun Also Rises", .before = text)

The_Old_Man_and_the_Sea_Hemingway_Ernest <- read_delim("The Old Man and the Sea_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
The_Old_Man_and_the_Sea_Hemingway_Ernest <- The_Old_Man_and_the_Sea_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Old Man and the Sea", .before = text)

For_Whom_the_Bell_Tolls_Hemingway_Ernest <- read_delim("For Whom the Bell Tolls_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
For_Whom_the_Bell_Tolls_Hemingway_Ernest <- For_Whom_the_Bell_Tolls_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "For Whom The Bell Tolls", .before = text)

A_Farewell_to_Arms_Hemingway_Ernest <- read_delim("A Farewell to Arms_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
A_Farewell_to_Arms_Hemingway_Ernest <- A_Farewell_to_Arms_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "A Farewell to Arms", .before = text)

@@

```{r tidy_fitzgerald}
#breaking up texts into words
tidy_fitzgerald <- fitzgerald_download %>% unnest_tokens(word, text) %>% anti_join(stop_words)
```

>>>>

```{r gutenberg_fitzgerald_works}
#finding texts by Fitzgerald on gutenberg
fitzgerald_text <- gutenberg_works(author == "Fitzgerald, F. Scott (Francis Scott)")
fitzgerald_text <- fitzgerald_text[-c(2,3), ]
```

```{r gutenberg_fitzgerald_download}
#downloading all the texts found
fitzgerald_download <- fitzgerald_text %>% 
                      gutenberg_download(meta_fields = c("title", "author"))
```
```{r import_Fitzgerald_books}
The_Great_Gatsby <- read_delim("The Great Gatsby_Fitzgerald, F. Scott (Francis Scott).txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
The_Great_Gatsby <- The_Great_Gatsby %>% mutate(author = "Fitzgerald, F. Scott (Francis Scott)", .after = text) %>% mutate(title = "The Great Gatsby", .before = author)

Tender_is_the_Night <- read_delim("Tender is the Night_Fitzgerald, F. Scott (Francis Scott).txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
Tender_is_the_Night <- Tender_is_the_Night %>% mutate(author = "Fitzgerald, F. Scott (Francis Scott)", .after = text) %>% mutate(title = "Tender is the Night", .before = author)
```

```{r create_Fitzgerald_corpus}
fitzgerald_download$gutenberg_id <- NULL
fitzgerald_corpus <- bind_rows(fitzgerald_download, The_Great_Gatsby, Tender_is_the_Night)
```

@@

The_Sun_Also_Rises_Hemingway_Ernest <- read_delim("The Sun Also Rises_Hemingway, Ernest.txt", 
    delim = "\t", quote = "\\\"", escape_double = FALSE, 
    trim_ws = TRUE)
The_Sun_Also_Rises_Hemingway_Ernest <- The_Sun_Also_Rises_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Sun Also Rises", .before = author)

The_Old_Man_and_the_Sea_Hemingway_Ernest <- read_delim("The Old Man and the Sea_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
The_Old_Man_and_the_Sea_Hemingway_Ernest <- The_Old_Man_and_the_Sea_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "The Old Man and the Sea", .before = author)

For_Whom_the_Bell_Tolls_Hemingway_Ernest <- read_delim("For Whom the Bell Tolls_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
For_Whom_the_Bell_Tolls_Hemingway_Ernest <- For_Whom_the_Bell_Tolls_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "For Whom The Bell Tolls", .before = author)

A_Farewell_to_Arms_Hemingway_Ernest <- read_delim("A Farewell to Arms_Hemingway, Ernest.txt", 
    delim = ".", quote = "\\\"", escape_double = FALSE)
A_Farewell_to_Arms_Hemingway_Ernest <- A_Farewell_to_Arms_Hemingway_Ernest %>% mutate(author = "Hemingway, Earnest", .after = text) %>% mutate(title = "A Farewell to Arms", .before = author)

@@

```{r tidy_fitzgerald}
#breaking up texts into words
tidy_fitzgerald <- fitzgerald_corpus %>% unnest_tokens(word, text) %>% anti_join(stop_words)
```
